
\documentclass{sb_cv}
 
%\usepackage[scale=0.9,top=4cm]{geometry}
%\vspace*{-5mm}

% adjust the page margins
%\setlength{\hintscolumnwidth}{20cm}                % if you want to change the width of the column with the dates
%\setlength{\hintscolumnheight}{20cm}
%\setlength{\makecvtitlenamewidth}{15cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...


% personal data
\name{Sergey}{Bashkirov}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{Address address address}{ZIP City California}{USA}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
%\address{Address address address}{ZIP CITY California}{USA}% optional, remove / comment the line
\email{litedictteam@gmail.com}                               % optional, remove / comment the line if not wanted
\phone[mobile]{+1~(415)~000~0000}                   % optional, remove / comment the line if not wanted
\break
%\homepage{ajnorton.com}                         % optional, remove / comment the line if not wanted
\social[github][github.com/z80]{github.com/z80}
\social[linkedin][www.linkedin.com/in/sergey-bashkirov]{www.linkedin.com/in/sergey-bashkirov}
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-15mm}

\section{Summary}
%Application software engineer with R\&D experience in software and firmware development related to Atomic Force Microscopy, Raman TERS imaging with active open source community participation is seeking for a full time position in application development.

Application software engineer with R\&D experience in software and firmware development for scientific devices with active open source community participation is seeking for a full time position in application development. Experienced in software and firmware development for Atomic Force Microscopy, semiconductor Kelvin probe analysis, Raman TERS imaging, electrochemistry, actuators control. I enjoy prototyping and problem solving process, adhere DP principle: don't choose one guess - try them all.

\vspace*{-3mm}
\section{Areas of expertise}
\cvdoubleitem{Programming}{Crossplatform, embedded programming, realtime algorithms, RTOS, embedded scripting, 2d/3d visualization}{Math}{2d/3d geometry, computer vision, machine learning, statistics, image processing}
\cvdoubleitem{AFM}{Contact, semicontact, Kelvin probe, MFM, PFM}{Raman}{Confocal Raman, coupled mapping, TERS imaging}

\vspace*{-3mm}
\section{Personal achievements}
\begin{itemize}
\item Created from scratch software for controlling Atomic Force Microscope.
\item Reduced AFM modes development time and eased prototyping by implementing scriptable GUI builder and hardware embedded real time scripting language.
\item Reduced hardware design time by making expandable stackable PCB solutions consisting of identical PCBs. Made it for pheumatics control and stepper motors control.
\item Simplified "find the same place" task for AFM after sample reinstallation by making video aligning and navigation by video mode.
\item Reorganaized production and supplies purchase processes by perforing statistical predictive contracts analysis. Made business control software for warehouse keeping, product assembling, purchasing and contracts tracking.
\item Achieved high precision with equipment made of low cost components by applying machine learning techniques to calibration process.
\end{itemize}



\vspace*{-3mm}
\section{Technical proficiencies}
\cvdoubleitem{Programming}{C, C++, Java, microcontroller assembler}{Scripting}{Lua, Ruby, Python, Maxima, SQL, R, Shell scripting}
\cvdoubleitem{Platforms}{Linux, Windows, ChibiOs, FreeRTOS}{Web technologies}{Ruby-on-rails4, Javascript, Bootstrap}
\cvdoubleitem{Frameworks}{Qt, Boost, Swing, WxWidgets}{Various}{PCB design, Spice simulation, electrical debugging, mature soldering skill}
\cvdoubleitem{Microcontroller series}{ST Cortex-M; Atmel AVR8; Analog Devices Shark DSP, NXP ARM7TDMI}{Prototyping}{Capable to rapidly prototype electromechanical software and/or firmware controlled solutions}
\cvdoubleitem{Visualization}{Widgets design, Spatial, 3D geometry, 2D/3D visualization}{Math}{Computer vision, Kalman filtering, machine learning, statistics, data, image processing }



\vspace*{-3mm}
\section{Most recent work experience}
\cventry{}{Software Engineer}{Aist-NT Inc.}{Novato, CA}{}{AFM software development, firmware development, image processing, AFM modes design, AFM-Raman coupling, actuators control, data acquisition and processing, production control}  % arguments 3 to 6 can be left empty


\cventry{}{Contract}{Transmag}{Santa Rosa, CA}{}{USB based BLDC motor controller's interface development. Designed firmware, user interface, suggested proper USB schematics.}

\cventry{}{Software engineer}{NT-Mdt}{Moscow, Russia}{}{Scanning probe microscope and auxilary devices programming. Designing drivers, firmware, user interface, algorithms.}




\vspace*{-3mm}
\section{Education}
\cventry{}{Master of Science in Applied Mathematics and Physics}{Moscow Institute of Physics and Technology}{Moscow, Russia}{}{}
\begin{itemize}
\item \textbf{Most recent courses taken:} Circuits \& Electronics, Machine learning, Autonomous navigation, Kalman filtering, SAAS, Statistics with R, Node.JS, Angular.JS, Booststrap, JavaScript.
\end{itemize}



\vspace*{-3mm}
\section{Open source projects participation}
\cvitemwithcomment{grambo-pi.com}{Created expandable stackable PCBs set for RaspberryPi computer for robot prototyping.}{}
\cvitemwithcomment{xonotic.org}{Created Blend2map Blender3D to MAP exporter.}{}
\cvitemwithcomment{chibios.org}{Submitted I2C slave mode driver, IWDG driver.}{}
\cvitemwithcomment{QtLua}{Provided a patch making Object::connect() work in the same way as in Qt.}{}
\cvitemwithcomment{Gaw}{Provided a patch fixing crashes with default configuration file for gaw waveform viewer.}{}



\end{document}



