\section{Summary}
Application software engineer with R\&D experience in software and firmware development for scientific devices with active open source community participation; experienced in GUI design, hardware to computer communication, firmware, RTOS, real time applications, motors control, pneumatics regulation, Atomic Force Microscopy, semiconductor Kelvin probe analysis, Raman TERS imaging, electrochemistry, BLDC, stepper motors, piezoceramics, actuators control; have experience in algorithms design, data acquisition and processing, computer vision, machine learning; rapid prorotyping and electrical debugging; good project management abilities, problem solving R\&D experience.

\vspace*{-4mm}
\section{Areas of expertise}
\cvdoubleitem{Crossplatform programming}{GUI, hardware communication}{RPC design}{Sockets, XMPP, ICE, XMLRPC}
\cvdoubleitem{Firmware design}{Real time firmware, actuators control, physical properties measurement, RTOS and bare metal firmware}{Scripting and automation}{Scripting languages, embedded scripting, bare metal firmware scripting}
\cvdoubleitem{Visualization}{Widgets design, Spatial, 3D geometry, 2D/3D visualization}{Math}{Computer vision, machine learning, statistics, data, image processing }

\vspace*{-4mm}
\section{Personal achievements}
\begin{itemize}
\item Created from scratch software for controlling Atomic Force Microscope.
\item Reduced AFM modes development time and eased prototyping by implementing scriptable GUI builder and hardware embedded real time scripting language.
\item Reduced hardware design time by making expandable stackable PCB solutions consisting of identical PCBs. Made it for pheumatics control and stepper motors control.
\item Simplified "find the same place" task for AFM after sample reinstallation by making video aligning and navigation by video mode.
\item Reorganaized production and supplies purchase processes by perforing statistical predictive contracts analysis. Made business control software for warehouse keeping, product assembling, purchasing and contracts tracking.
\item Achieved high precision with equipment made of low cost components by applying machine learning techniques to calibration process.
\end{itemize}

\vspace*{-4mm}
\section{Technical proficiencies}
\cvdoubleitem{Programming}{C, C++, Java, microcontroller assembler}{Scripting}{Lua, Ruby, Python, R, SQL, Shell scripting}
\cvdoubleitem{Platforms}{Linux, Windows, ChibiOs, FreeRTOS}{Web technologies}{Ruby-on-rails4, Javascript, Bootstrap}
\cvdoubleitem{Frameworks}{Qt, Boost, Swing, WxWidgets}{Various}{FTDI/CPLD Verilog simulation, PCB design, electrical debugging, soldering skill}
\cvdoubleitem{Devices}{Avr8, Cortex-M, NXP ARM7TDMI, AD Shark DSP, Altera FPGA/CPLD}{Aplications}{Stepper, BLDC, DC motors control; piezoceramics, temperature, humidity control, data acquisition, signal processing, filtering, automation}

\vspace*{-4mm}
\section{Most recent work experience}
\cventry{}{Software Engineer}{Aist-NT Inc.}{Novato, CA}{}{AFM software development, firmware development, image processing, AFM modes design, AFM-Raman coupling, actuators control, data acquisition and processing, production control}  % arguments 3 to 6 can be left empty



\cventry{}{Contractor}{Transmag}{Santa Rosa, CA}{}{USB based BLDC motor controller's interface development. Designed firmware, user interface, suggested proper USB schematics.}

\vspace*{-4mm}
\section{Education}
\cventry{}{Master of Science in Applied Mathematics and Physics}{Moscow Institute of Physics and Technology}{Moscow, Russia}{}{}
\begin{itemize}
\item \textbf{Most recent courses taken:} Circuits \& Electronics, Machine learning, SAAS, Kalman filtering, Autonomous navigation, Statistics with R, Node.JS, Angular.JS, Booststrap, JavaScript.
\end{itemize}